---
title: Stream temperatures
author: Charlotte Wickham
output: pdf_document
---

```{r setup, message = FALSE}
library(tidyverse)
library(lubridate)
knitr::opts_chunk$set(fig.height = 3)
```

Explore stream temperatures for the sites:

* GSWS01 Andrews Lookout Creek Gaging Station	
* GSMACK Andrews Mack Creek Gaging Station	 
* GSWS01 Andrews Watershed 1 Gaging Station	  	

## Data Import

```{r, message = FALSE}
streams <- read_csv("data/HT00441_v8.csv")
names(streams) <- tolower(names(streams))
```

## GSLOOK

Get site data:
```{r}
gslook <- streams %>% 
  filter(sitecode == "GSLOOK")
```

Filter for quality and time period:
```{r}
gslook <- gslook %>%
  filter(year(date) > 2000, year(date) < 2020) %>%   
  mutate(
    watertemp_mean_day = ifelse(watertemp_mean_flag != "A", 
      NA, watertemp_mean_day)) %>% 
  select(sitecode, date, watertemp_mean_day, watertemp_method) 
```

Checks on data quality/coverage:
```{r}
gslook %>% 
  summarise(
    n_obs = n(),
    n_days = n_distinct(date),
    n_missing = sum(is.na(watertemp_mean_day))
  )
```
Plot site stream temperature over time:
```{r}
gslook %>% 
  ggplot(aes(date, watertemp_mean_day)) + 
  geom_line(aes(color = watertemp_method)) +
  scale_color_brewer("Method", palette = "Set2") +
  labs(x = "", y = "Water temperature (C)",
    title = "GSLOOK")
```

## GSMACK

Get site data:
```{r}
gsmack <- streams %>% 
  filter(sitecode == "GSMACK")
```

Filter for quality and time period:
```{r}
gsmack <- gsmack %>%
  filter(year(date) > 2000, year(date) < 2020) %>%   
  mutate(
    watertemp_mean_day = ifelse(watertemp_mean_flag != "A", 
      NA, watertemp_mean_day)) %>% 
  select(sitecode, date, watertemp_mean_day, watertemp_method) 
```

Checks on data quality/coverage:
```{r}
gsmack %>% 
  summarise(
    n_obs = n(),
    n_days = n_distinct(date),
    n_missing = sum(is.na(watertemp_mean_day))
  )
```
Plot site stream temperature over time:
```{r}
gsmack %>% 
  ggplot(aes(date, watertemp_mean_day)) + 
  geom_line(aes(color = watertemp_method)) +
  scale_color_brewer("Method", palette = "Set2") +
  labs(x = "", y = "Water temperature (C)",
    title = "GSMACK")
```

## GSWS01

Get site data:
```{r}
gsws01 <- streams %>% 
  filter(sitecode == "GSWS01")
```

Filter for quality and time period:
```{r}
gsws01 <- gsws01 %>%
  filter(year(date) > 2000, year(date) < 2020) %>%   
  mutate(
    watertemp_mean_day = ifelse(watertemp_mean_flag != "A", 
      NA, watertemp_mean_day)) %>% 
  select(sitecode, date, watertemp_mean_day, watertemp_method) 
```

Checks on data quality/coverage:
```{r}
gsws01 %>% 
  summarise(
    n_obs = n(),
    n_days = n_distinct(date),
    n_missing = sum(is.na(watertemp_mean_day))
  )
```
Plot site stream temperature over time:
```{r}
gsws01 %>% 
  ggplot(aes(date, watertemp_mean_day)) + 
  geom_line(aes(color = watertemp_method)) +
  scale_color_brewer("Method", palette = "Set2") +
  labs(x = "", y = "Water temperature (C)",
    title = "GSWS01")
```
